---
title: | 
 | PASS1A/PASS1C Metabolomics: 
 | UMich PASS1A (Original PASS1A) Data Structure
author: "Alec Steep"
date: "11/26/2021"
always_allow_html: true
output: 
  html_document:
    toc: true
    code_folding: hide
    highlight: zenburn
    css: ../../style/style.css
---

# CONFIGURATIONS
```{r setup, message=FALSE, results='hide', warning = FALSE, echo = TRUE}
# Set the working directory and tool paths on your local computer.
WD <- '/Users/Alec/motrpac/20210826_pass1c-umich'
# Set the gsutil path

knitr::opts_knit$set(root.dir=WD)
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(cache = FALSE)
```

##### CSS Top Styling
```{r CSS Top Styling}
writeLines("td, th { padding : 3px } th { background-color:white; color:black; border:1px solid black; text-align:center } td {color:black; border:1px solid black; word-wrap:break-word; white-space:nowrap; overflow: hidden; text-overflow: ellipsis; max-width:300px; text-align:left}", con=file.path(normalizePath(WD), "style/style.css"))
```

##### Overview

# Prepare Environment

## Setup the Environment
```{r Setup the Environment, message=FALSE, results='hide', warning = FALSE, echo = TRUE}
################################################################################
##### Resources and Dependencies ###############################################
################################################################################
# Whether to knit document and display data
knit_time = TRUE

# Load dependencies
pacs...man <- c("tidyverse","kableExtra","devtools","MotrpacBicQC","impute","glue")
for(pac in pacs...man){
  suppressWarnings(suppressPackageStartupMessages(library(pac, character.only = TRUE)))
}

#browseVignettes("MotrpacBicQC")
############################################################
##### Functions ############################################
############################################################

# Name functions
select <- dplyr::select
map <- purrr::map
desc <- dplyr::desc
arrange <- dplyr::arrange
melt <- reshape2::melt
mutate <- dplyr::mutate
glue <- glue::glue

# Global options
options(dplyr.print_max = 100)
options(scipen=10000)

# Colors
redblue100<-rgb(read.table(paste0(WD,'/colors/redblue100.txt'),sep='\t',row.names=1,header=T))
```

# Phenotypic Data

## Adjust the Phenotype Data 
```{r}
# Phenotype Data (1A)
#########################
pheno_file <- glue("{WD}/data/20201021_pass1a-06-pheno-viallabel_steep.txt")
pheno_df1a <- read.csv(pheno_file, header = T, sep = '\t')
pheno_df1a <- pheno_df1a %>%
  mutate(tissue = case_when(Specimen.Processing.sampletypedescription == 'Brown Adipose' ~ 'badi',
                            Specimen.Processing.sampletypedescription == 'EDTA Plasma' ~ 'pla',
                            Specimen.Processing.sampletypedescription == 'Gastrocnemius' ~ 'gas',
                            Specimen.Processing.sampletypedescription == 'Heart' ~ 'hrt',
                            Specimen.Processing.sampletypedescription == 'Kidney' ~ 'kid',
                            Specimen.Processing.sampletypedescription == 'Liver' ~ 'liv',
                            Specimen.Processing.sampletypedescription == 'Lung' ~ 'lun',
                            Specimen.Processing.sampletypedescription == 'White Adipose' ~ 'wadi',
                            Specimen.Processing.sampletypedescription == 'PaxGene RNA' ~ 'pax',
                            Specimen.Processing.sampletypedescription == 'Hippocampus' ~ 'hip',
                            Specimen.Processing.sampletypedescription == 'Cortex' ~ 'cor',
                            Specimen.Processing.sampletypedescription == 'Hypothalamus' ~ 'hyp',
                            Specimen.Processing.sampletypedescription == 'Vastus Lateralis' ~ 'vas',
                            Specimen.Processing.sampletypedescription == 'Tibia' ~ 'tib',
                            Specimen.Processing.sampletypedescription == 'Aorta' ~ 'aor',
                            Specimen.Processing.sampletypedescription == 'Small Intestine' ~ 'sma',
                            Specimen.Processing.sampletypedescription == 'Adrenals' ~ 'adr',
                            Specimen.Processing.sampletypedescription == 'Colon' ~ 'col',
                            Specimen.Processing.sampletypedescription == 'Spleen' ~ 'spl',
                            Specimen.Processing.sampletypedescription == 'Testes' ~ 'tes',
                            Specimen.Processing.sampletypedescription == 'Ovaries' ~ 'ova'))
pheno_df1a$viallabel <- as.character(pheno_df1a$viallabel)

# Save data
pheno_file <- glue("{WD}/data/20211215_pass1a-06-pheno-viallabel_steep.txt")
# write.table(pheno_df1a, file = pheno_file, quote = FALSE, sep = '\t', row.names = FALSE)
```


# Load Data Abundance Data

## Load the PASS1A metabolomics datasets from before and create data matrices
```{r}
# Load the prior pass1a data (takes a few minutes)
pass1a_nested_file <- glue("{WD}/../20200915_metabolomics-pass1a/data/20201010_pass1a-metabolomics-countdata-nested_steep.rds")
pass1a_df <- readRDS(pass1a_nested_file)
#dim(pass1a_df)
#head(pass1a_df)
```

# Partition Data into NxP Matrices

## Create Data Matrices (UM rppos)
```{r}
# Plasma
pla_rppos_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rppos') %>%
  filter(TISSUE == 'plasma') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Plasma
hip_rppos_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rppos') %>%
  filter(TISSUE == 'hippocampus') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Plasma
gas_rppos_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rppos') %>%
  filter(TISSUE == 'gastrocnemius') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix() 

# Plasma
hrt_rppos_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rppos') %>%
  filter(TISSUE == 'heart') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Plasma
kid_rppos_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rppos') %>%
  filter(TISSUE == 'kidney') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Plasma
lun_rppos_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rppos') %>%
  filter(TISSUE == 'lung') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Plasma
liv_rppos_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rppos') %>%
  filter(TISSUE == 'liver') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Plasma
badi_rppos_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rppos') %>%
  filter(TISSUE == 'brown-adipose') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Plasma
wadi_rppos_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rppos') %>%
  filter(TISSUE == 'white-adipose') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()
```

## Create Data Matrices (UM rpneg)
```{r}
# Plasma
pla_rpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rpneg') %>%
  filter(TISSUE == 'plasma') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Hippocampus
hip_rpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rpneg') %>%
  filter(TISSUE == 'hippocampus') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Gastrocnemius
gas_rpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rpneg') %>%
  filter(TISSUE == 'gastrocnemius') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Heart
hrt_rpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rpneg') %>%
  filter(TISSUE == 'heart') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Kidney
kid_rpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rpneg') %>%
  filter(TISSUE == 'kidney') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Lung
lun_rpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rpneg') %>%
  filter(TISSUE == 'lung') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Liver
liv_rpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rpneg') %>%
  filter(TISSUE == 'liver') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Badi
badi_rpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rpneg') %>%
  filter(TISSUE == 'brown-adipose') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# Wadi
wadi_rpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'rpneg') %>%
  filter(TISSUE == 'white-adipose') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()
```

## Create Data Matrices (UM ionpneg)
```{r}
# Plasma
pla_ionpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'ionpneg') %>%
  filter(TISSUE == 'plasma') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# hip
hip_ionpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'ionpneg') %>%
  filter(TISSUE == 'hippocampus') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# gas
gas_ionpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'ionpneg') %>%
  filter(TISSUE == 'gastrocnemius') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# hrt
hrt_ionpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'ionpneg') %>%
  filter(TISSUE == 'heart') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# kid
kid_ionpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'ionpneg') %>%
  filter(TISSUE == 'kidney') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# lun
lun_ionpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'ionpneg') %>%
  filter(TISSUE == 'lung') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# liv
liv_ionpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'ionpneg') %>%
  filter(TISSUE == 'liver') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# badi
badi_ionpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'ionpneg') %>%
  filter(TISSUE == 'brown-adipose') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()

# wadi
wadi_ionpneg_pass1a.0 <- pass1a_df %>%
  filter(STUDY_INSTITUTE == 'University of Michigan') %>%
  filter(NAMED == 'named') %>%
  filter(DATASET == 'untargeted') %>%
  filter(METAB_FAMILY == 'ionpneg') %>%
  filter(TISSUE == 'white-adipose') %>%
  select(COUNT_DATA) %>%
  unnest(COUNT_DATA) %>%
  select(viallabel, METABOLITE_NAME, VALUE) %>%
  pivot_wider(names_from = METABOLITE_NAME, values_from = VALUE) %>%
  column_to_rownames(var = 'viallabel') %>%
  as.matrix()
```

# Save Data

## Save the Matrices in .RData Files
```{r}
# UM-rppos
save(pla_rppos_pass1a.0, hrt_rppos_pass1a.0, lun_rppos_pass1a.0, liv_rppos_pass1a.0,
     gas_rppos_pass1a.0, kid_rppos_pass1a.0, wadi_rppos_pass1a.0, badi_rppos_pass1a.0,
     hip_rppos_pass1a.0, file = glue("{WD}/data/UM-rppos/UM_rppos.0.RData"))

# UM-rpneg
save(pla_rpneg_pass1a.0, hrt_rpneg_pass1a.0, lun_rpneg_pass1a.0, liv_rpneg_pass1a.0,
     gas_rpneg_pass1a.0, kid_rpneg_pass1a.0, wadi_rpneg_pass1a.0, badi_rpneg_pass1a.0,
     hip_rpneg_pass1a.0, file = glue("{WD}/data/UM-rpneg/UM_rpneg.0.RData"))

# UM-ionpneg
save(pla_ionpneg_pass1a.0, hrt_ionpneg_pass1a.0, lun_ionpneg_pass1a.0, liv_ionpneg_pass1a.0,
     gas_ionpneg_pass1a.0, kid_ionpneg_pass1a.0, wadi_ionpneg_pass1a.0, badi_ionpneg_pass1a.0,
     hip_ionpneg_pass1a.0, file = glue("{WD}/data/UM-ionpneg/UM_ionpneg.0.RData"))
```

# Session Info
```{r Sesh}
warnings()
session_info()
```

`r knitr::knit_exit()`
